Simulation Summary Figures

### 2018-08-09 datasets/simulations/simulations-summary.Rmd
Plot sampling dist effect with cubic covariate to see bl
Change sim plot panel letters

gp <- plot_grid(null_tnr_diff + guides(color = FALSE, linetype = FALSE),
                null_fwer_diff + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(null_tnr_diff), rel_widths = c(1, 1/16))
gp
```

@@

```{r, fig.width = 18, fig.height = 8}
res_noise <- dplyr::filter(resmet, setting == "informative-cosine")

@@

gp <- plot_grid(noise_fdr_diff + guides(color = FALSE, linetype = FALSE),
                noise_tpr_diff + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(noise_tpr_diff), rel_widths = c(1, 1/16))
gp
```

@@

gp <- plot_grid(icov_fdr_diff + guides(color = FALSE, linetype = FALSE),
                icov_tpr_diff + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 1)
gp <- plot_grid(gp, get_legend(icov_tpr_diff), rel_widths = c(1, 1/12))
gp
```

@@

gp <- plot_grid(info_fdr_diff + guides(color = FALSE, linetype = FALSE),
                info_tpr_diff + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 2)
gp <- plot_grid(gp, get_legend(info_tpr_diff), rel_widths = c(1, 1/8))
gp
```

>>>>

gp <- plot_grid(null_tnr_diff + guides(color = FALSE, linetype = FALSE),
                null_fwer_diff + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[3:4], ncol = 1)
gp <- plot_grid(gp, get_legend(null_tnr_diff), rel_widths = c(1, 1/16))
gp
```

@@

```{r, fig.width = 18, fig.height = 8}
res_noise <- dplyr::filter(resmet, setting == "informative-cubic")

@@

gp <- plot_grid(noise_fdr_diff + guides(color = FALSE, linetype = FALSE),
                noise_tpr_diff + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[3:4], ncol = 1)
gp <- plot_grid(gp, get_legend(noise_tpr_diff), rel_widths = c(1, 1/16))
gp
```

@@

gp <- plot_grid(icov_fdr_diff + guides(color = FALSE, linetype = FALSE),
                icov_tpr_diff + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[3:4], ncol = 1)
gp <- plot_grid(gp, get_legend(icov_tpr_diff), rel_widths = c(1, 1/12))
gp
```

@@

gp <- plot_grid(info_fdr_diff + guides(color = FALSE, linetype = FALSE),
                info_tpr_diff + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[3:4], ncol = 2)
gp <- plot_grid(gp, get_legend(info_tpr_diff), rel_widths = c(1, 1/8))
gp
```
